### 2019-01-29 manuscript.tex
Update manuscript.tex

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.  In addition, interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10, WahlEsse18}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position. This paragraph is to briefly present fgc in context.}

\cfcmt{Culture and tradtions are guarded as main reason for FGC practice \cite{PariSaru18}, more cites}There are at least three main theoretical perspectives from outside the FGC communities shedding lights on the complexities of FGC \cite{Hayf05, Youn02}: social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.) Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}. When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

Modernization
theory proposes that traditional social relationships and values
would be eroded by modernization (e.g., with the improvement of
wealth and education and emphasis of individual rights)
(see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?). There is a wide
range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95})
and woman's empowerment on making FGC decision are shared concerns:
for example, from social position \cite{VanMeek15}, autonomy
\cite{Meye00}, gender equality and human rights \cite{Drol11}, to
gender identity \cite{Youn04, Koom14, WintKoom09}. Although
convention theory was well studied and showed a larger effect on FGC
practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10,
FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06,
ReigGonz14, YirgKass12}), these theories did not necessarily excluded
each other, especially between modernization theory and feminist
theory \cite{Hayf05}.

@@

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes towards FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intenation can be detected at both a population and a community level.  If so, if social norms the most soundly

Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why) 
\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.} \cf{reframed the main question.}
\jd{I guess this is also a good place to discuss our community variables?}

@@

Tables and figures including:
table of basic sociodemographic results
figure:  proportion of FGC daughters and FGC future
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% figure of significant variables on modernization and pile the findings of the 4 nations into one figure.
% a chart like figure 8-8D \cite{UNCI13}
% figure of FGC prevalence by age and country (see Hayf05)
% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuity.

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{Shel-Wand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

@@

% get info on legal situation of FGC in those countries

@@

>>>>

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of intervening and abolishing	the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.

@@

Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).

\subsection{Research Questions}\label{research-questions}

The main model is the “daughter” model, which analyzed associations of attitude (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s attitudes of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of attitudes of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positionss change the main model.

\jd{I guess this is also a good place to discuss our community variables?}

@@

Tables and figures including:
table of basic sociodemographic results
figure:  proportion of FGC daughters and FGC future
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% figure of significant variables on modernization and pile the findings of the 4 nations into one figure.
% a chart like figure 8-8D \cite{UNCI13}
% figure of FGC prevalence by age and country (see Hayf05)
% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuance.

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{Shel-Wand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination,” for marital market.  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

@@

“we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families. Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}
% get info on legal situation of FGC in those countries

@@

systematic review of effectiveness of fgc factors associating the practice \cite{WaigDoos18}
